### 2019-03-08 paper/sex_selection_spacing-ver2.tex
Add region bootstrap graphs

@@

\FloatBarrier
\section{Conclusion\label{sec:conclusion}}

>>>>

\FloatBarrier

@@

\begin{figure}[htpb]
\centering
\caption*{Urban}
\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell2_high_urban_r1}} 
\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell3_high_urban_r1}} 
\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell4_high_urban_r1}} 
\\
\caption*{Rural}
\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell2_high_rural_r1}} 
\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell3_high_rural_r1}} 
\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell4_high_rural_r1}} 
\caption{high education - r1}
\end{figure}

\begin{figure}[htpb]
\centering
\caption*{Urban}
\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell2_high_urban_r2}} 
\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell3_high_urban_r2}} 
\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell4_high_urban_r2}} 
\\
\caption*{Rural}
\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell2_high_rural_r2}} 
\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell3_high_rural_r2}} 
\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell4_high_rural_r2}} 
\caption{high education - r2}
\end{figure}

\begin{figure}[htpb]
\centering
\caption*{Urban}
\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell2_high_urban_r3}} 
\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell3_high_urban_r3}} 
\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell4_high_urban_r3}} 
\\
\caption*{Rural}
\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell2_high_rural_r3}} 
\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell3_high_rural_r3}} 
\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell4_high_rural_r3}} 
\caption{high education - r3}
\end{figure}

\begin{figure}[htpb]
\centering
\caption*{Urban}
\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell2_high_urban_r4}} 
\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell3_high_urban_r4}} 
\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell4_high_urban_r4}} 
\\
\caption*{Rural}
\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell2_high_rural_r4}} 
\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell3_high_rural_r4}} 
\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell4_high_rural_r4}} 
\caption{high education - r4}
\end{figure}

\section{Conclusion\label{sec:conclusion}}
